Verifying Demonstrations

### 2021-06-17 paper/system-model.tex
merges sybil footnotes in system model

Throughout this paper, each time we refer to a participant, such as Alice, we 
actually mean a personal device that can perform cryptographic operations and 
communicate with other local devices on Alice's behalf.
Furthermore, we assume that each participant has a digital identity certificate signed 
by \iac{CA}\footnote{%
  We note that any system that prevents Sybil attacks~\cite{SybilAttack} will 
  do.
} that ensures a one-to-one mapping between an identity and a cryptographic 
key\footnote{%
  For every physical person there exists at most one valid digital certificate.
}.

>>>>

Throughout this paper, each time we refer to a participant, such as Alice, we 
actually mean a personal device that can perform cryptographic operations and 
communicate with other local devices on Alice's behalf.
Furthermore, we assume that each participant has a digital identity certificate signed 
by \iac{CA} that ensures a one-to-one mapping between an identity and
a cryptographic key\footnote{%
  For every physical person there exists at most one valid digital
  certificate. 
  We note that any system that prevents Sybil attacks~\cite{SybilAttack} will 
  do. 
}.
